Your Title Goes Here

### 2017-12-31 documentation/documentation.tex
correcting some typers

\subsection{Methodology}
This documentation consists out of seven chapters. The first five chapters are going to be discussed, as they are relevant for the reproduction of the results. The first chapter contains a short introduction and provides the reader with an overview of the topic. Furthermore, it points out the relevance of the documentation. In the second chapter the requirements (setup) is discussed to enable the reproducibility and run the own written code scripts in Python. Python has been used as it was suggested in the course Software Engineering for Economists. The third chapter discusses the input data. This includes the process of gathering and storing twitter tweets as well as the gathering of the bitcoin price data. The data have been gathered by using Application Programming Interfaces (API)to ensure high quality of the data. The fourth chapter discusses how the data is aggregated wrangled to enable the subsequent analysis. The fifth chapter explains how the analysis has been conducted whit STATA.

>>>>

\subsection{Methodology}
This documentation consists out of seven chapters. The first five chapters are going to be discussed, as they are relevant for the reproduction of the results. The first chapter contains a short introduction and provides the reader with an overview of the topic. Furthermore, it points out the relevance of the documentation. In the second chapter the requirements (setup) are discussed to enable the reproducibility and run the own written code scripts in Python. Python has been used as it was suggested in the course Software Engineering for Economists. The third chapter discusses the input data. This includes the process of gathering and storing twitter tweets as well as the gathering of the bitcoin price data. The data have been gathered by using Application Programming Interfaces (API) to ensure high quality of the data. The fourth chapter discusses how the data is aggregated wrangled to enable the subsequent analysis. The fifth chapter explains how the analysis has been conducted whit STATA.
